Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-26 Docs/IJES/journal.tex
review 5.1 Experimental Setup

\textcolor{blue}{We have to point out that the experimental results presented here depend on the computer's processor and memory, the version of each tool (MATLAB and ESBMC), and the partitioning problem to be solved. Additionally, any change from MATLAB to another tool or to GA/ILP libraries for different programming languages can influence the measured time of the algorithms.}

@@

Based on the \textcolor{blue}{mean,} standard deviation and tolerance interval to each set of time sample, it was obtained a \textcolor{blue}{confidence level} of $91.7$\% to ESBMC (sequential, SS, PB and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA. A timeout condition (TO) is reached when the verification time is longer than $3600$ seconds. A memory-out (MO) occurs when the tool reaches $15$ GB of memory. \textcolor{blue}{The TO was defined based on previous empirical tests as well, where a larger TO ({\it e.g.}, $5000$ seconds) did not produce substantial differences in the experimental results.}

>>>>

\textcolor{blue}{Note that the experimental results presented here depend on the computer's processor and memory, the version of each tool (MATLAB and ESBMC), and the partitioning problem to be solved. Additionally, any change from MATLAB to another tool or to GA/ILP libraries for different programming languages can influence the measured time of the algorithms.}

@@

Based on the \textcolor{blue}{mean,} standard deviation and tolerance interval to each set of time sample, it was obtained a \textcolor{blue}{confidence level} of $91.7$\% to ESBMC (sequential, SS, PB, and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA. A timeout condition (TO) is reached when the verification time is longer than $3600$ seconds. A memory-out (MO) occurs when the tool reaches $15$ GB of memory. \textcolor{blue}{The TO was defined based on previous empirical tests as well, where a larger TO ({\it e.g.}, $5000$ seconds) did not produce substantial differences in the experimental results.}
